More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-10-10 2016-Weak-FH-Bisim/WeakBisim.tex
sketch of proof for discussion

\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  \\
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
There exist  sets of $\beta^1_i$, $\beta^2_i$, and $\beta^3_i$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
 \end{mathpar}
If only if there exist a set of $\beta$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\overline{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

@@

\end{corollary}

\begin{lemma}
Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
If $A_1$ and $A_2$ are weak FH-bisimilar then 
\begin{itemize}
 \item  For any weak open transition $\symb{WOT} \in \WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

@@

\TODO{Underneath is the rules of the closed semantics. Not sure we
  should keep them here, but we mentionned we should have a proof of
  the relation between the 2 semantics... In an extended version I
  suppose (;-)}

>>>>

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  \\
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
There exist  sets of $\beta^1_i$, $\beta^2_i$, and $\beta^3_i$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
 \end{mathpar}
If only if there exist a set of $\beta$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\overline{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

@@

\end{corollary}
\begin{proof}
Sketch for discussion.\\

1) By lemma \ref{lem-rel-OT-WOT} we have:

\begin{mathpar}
\openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
         \implies

 \Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) 
 \end{mathpar}
2) From Definition \ref{def-Weak-bisim} we have:

For each open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

 3) From Definition \ref{def:buildweakOT} we have:

 \begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \overline{\gamma_1}\dotcup \overline{\gamma_2}\dotcup\overline{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'} \in\WT
} \WTTrois
\end{mathpar}

 \TODO{Trouver comment decrire la recurrence/fusionner les Pred}

\end{proof}
------------------------------------------------------
\begin{lemma}
Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
If $A_1$ and $A_2$ are weak FH-bisimilar then 
\begin{itemize}
 \item  For any weak open transition $\symb{WOT} \in \WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

@@

\TODO{Underneath is the rules of the closed semantics. Not sure we
  should keep them here, but we mentioned we should have a proof of
  the relation between the 2 semantics... In an extended version I
  suppose (;-)}
